The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-20 ms.Rmd
resolving figure legend issues & adding higher resolution figures

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = FALSE}
# set up knitr options
opts_chunk$set(fig.path = 'figs/',
               message = FALSE,
               dev = c('png'),
               cache = TRUE)

@@

```{r plotzoonoverviewcaptions, eval = TRUE, echo = FALSE}
pzocap <- "
The modular SDM structure encoded by a zoon workflow. A) Flow diagram representing the module types. B) The required inputs and outputs for each module types (full details given in the `zoon` vignette 'Building a module'). C) Chaining and listing modules of the same type. D) The structure of a workflow object.\\label{fig:workflows}
"
```

```{r plotzoonoverview, echo = FALSE, fig.height = 9, dpi = 300, fig.cap = pzocap}

@@

  # add a panel letter
  mtext(text = LETTERS[i],
        side = 3,
        line = 0.5,
        adj = 0)  
}
```

@@

```{r fengworkflow, eval = TRUE, results = 'hide', fig.show = 'hide', message = FALSE}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))

@@

![Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence (darker blue showing higher probability of occurrence). White areas are masked due to being marine in the marine environment or due to the MESS mask.\label{fig:fengmap](./figs/fengworkflow-1.png)

>>>>

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = TRUE}
# set up knitr options
knitr::opts_chunk$set(fig.path = 'figs/',
               message = FALSE,
               dev = c('png'),
               cache = TRUE)
```

@@

```{r plotzoonoverview, echo = FALSE, fig.show = 'hide', fig.height = 9, dpi = 300}

@@

  # add a panel letter
  mtext(text = LETTERS[i],
        side = 3,
        line = 0.5,
        adj = 0)  
}
```
![The modular SDM structure encoded by a zoon workflow. A) Flow diagram representing the module types. B) The required inputs and outputs for each module types (full details given in the `zoon` vignette 'Building a module'). C) Chaining and listing modules of the same type. D) The structure of a workflow object.\label{fig:workflows}](./figs/plotzoonoverview-1.png)

@@

```{r fengworkflow, eval = TRUE, dpi = 300, fig.show = 'hide', message = FALSE}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))

@@

![Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence (darker blue showing higher probability of occurrence). White areas are masked due to being marine in the marine environment or due to the MESS mask.\label{fig:fengmap}](./figs/fengworkflow-1.png)
